\documentclass[12pt,a4paper]{article}

%%% REPORT FOR SPIN WAVES EXCITATION BY ACOUSTIC PULSE

\usepackage{amsmath}               %AMSMath tools for flexible equations
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{cite}
\usepackage[margin=1.5cm]{geometry}
\usepackage{subfig} % remplace subfigure
%\usepackage[utf8x]{inputenc} 
\usepackage[latin1]{inputenc} 
\usepackage[T1]{fontenc} 
\usepackage[section]{placeins}
\usepackage{listings} % in order to include code in a tex file
\usepackage{setspace}
\usepackage{hyperref}
\onehalfspacing

%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\thefootnote}{\arabic{footnote}}
\DeclareTextSymbol{\degre}{T1}{6}

\newcommand{\valentin}{\textsc{Valentin} }
\newcommand{\vladimir}{\textsc{Vladimir} }
\newcommand{\anton}{\textsc{Anton} }
\newcommand{\alexandr}{\textsc{Alexandr} }
\newcommand{\vasily}{\textsc{Vasily} }

	
\begin{document}
	
	
\begin{center}
	{\bf\Large Meeting Recap~\MakeUppercase{\romannumeral 13}}\\
	{\bf\Large \today}\\
	\vspace{0.4cm}
	{\large Valentin \textsc{Besse}\footnote{Author of the report}, Vladimir \textsc{Vlasov}, Anton \textsc{Golov}, Alexandr \textsc{Alekhin} and Vasily \textsc{Temnov}}\\
	\vspace{0.6cm}
	%{\large \today}
	%{\large August 28, 2017}
\end{center}
\vspace{0.1cm}

\section*{Version}

\begin{itemize}
    \item September 28, 2017: V1.
\end{itemize}

\section*{Present at the meeting}

\begin{itemize}
    \item Valentin \textsc{Besse}.
    \item Vladimir \textsc{Vlasov}.
    \item Anton \textsc{Golov}.
\end{itemize}

\section*{Progress}

\begin{table}[ht]
    \centering
    \begin{tabular}{|l|l|}
    \hline
    Tasks & Status \\
    \hline
    \hline
    Figures/Tables & Figures are almost done. We use figures from Rome's presentation. \\
    \hline
    Summary statements & To be done\\
    \hline
    Scientific audience & We target PRL\\
    \hline
    Materials and methods & To be done\\
    \hline
    Re-evalutate data & To be done\\
    \hline
    Results & To be done\\
    \hline
    Discussion/Conclusion & To be done\\
    \hline
    References & To be done\\
    \hline
    Introduction & To be done\\
    \hline
    Title & Acousto-magnonic cavity with exchange magnon in the THz regime\\
    \hline
    Conclusion paragraph & To be done \\
    \hline
    \end{tabular}
    \caption{Sum up of the tasks and the progress. The tasks' division follows the algorithm describe in Fig. 1 of \cite{o2009algorithm}}
    \label{tab:my_label}
\end{table}

\section*{Agenda}

During this meeting we discuss about:
\begin{enumerate}
    \item Rome presentation.
    \item Works to be done.
    \item Suggestions.
\end{enumerate}

%The pad used during the meeting can be found \href{https://pad.aumbox.net/mypads/?/mypads/group/exchange-magnons-4m3cvuz/pad/view/2017-09-28-meeting-9857vtq}{here}\footnote{https://pad.aumbox.net/mypads/?/mypads/group/exchange-magnons-4m3cvuz/pad/view/2017-09-28-meeting-9857vtq}.

\section{Works to be done}

\valentin will use the following pictures from Rome's presentation:
\begin{itemize}
    \item p.11, a temporal trace but in the case of a sample with 30 nm of thickness.
    \item p.22, a spectrum with the corresponding dispersion curves but for phase and frequency matching conditions.
    \item p.26, spectra for phase and frequency matching conditions for different number of acoustic pulses.
    \item p.30, spectra for phase and frequency matching conditions for different type of acoustic pulses.
    \item p.36, spectra for phase and frequency matching conditions for different values of the damping.
\end{itemize}

\section{Suggestions}

\valentin thinks that there is no need of supplementary simulation for the paper at the moment.
So \valentin suggests that Anton should start to work on simulations:
\begin{itemize}
    \item with magnetic anisotropy. Do we have paper about it in nickel ? I found two papers\footnote{\href{http://iopscience.iop.org/article/10.1088/0370-1328/78/1/305/pdf}{Magnetic Anisotropy in Single-crystal Nickel Films}}\footnote{\href{https://link.springer.com/content/pdf/10.1007\%2FBF01106052.pdf}{Magnetic Anisotropy of Nickel Films Produced by Chemical Reduction}}
    \item or other type of anisotropy.
    \item or with a varying magnetoelastic effect. Is this realist ? Is there any paper about it ?
\end{itemize}
What do you think about it ?

\section*{Next meeting}

The next meeting will be Monday November 6th at 2:00 pm (CET).

\newpage

\section*{List of abbreviations}

\begin{table}[ht]
    %\centering
    \begin{tabular}{ l c r }
        Landau-Lifschitz-Gilbert & $\Longrightarrow$ & LLG \\
        Ferromagnetic resonance & $\Longrightarrow$ & FMR \\
    \end{tabular}
\end{table}

\bibliographystyle{ieeetr}
\bibliography{Exchange_Magnons}

\end{document}