\documentclass[12pt,a4paper]{article}

%%% REPORT FOR SPIN WAVES EXCITATION BY ACOUSTIC PULSE

\usepackage{amsmath}               %AMSMath tools for flexible equations
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{cite}
%\usepackage[margin=1.5cm]{geometry}
\usepackage{fullpage}   % Texte en pleine page, réduction des marges 
\usepackage{subfig} % remplace subfigure
%\usepackage[utf8x]{inputenc} 
\usepackage[latin1]{inputenc} 
\usepackage[T1]{fontenc} 
\usepackage[section]{placeins}
\usepackage{listings} % in order to include code in a tex file
\usepackage{setspace}
\onehalfspacing
\usepackage{hyperref}


%\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\renewcommand{\thefootnote}{\arabic{footnote}}
\DeclareTextSymbol{\degre}{T1}{6}

\newcommand{\valentin}{\textbf{Valentin}}
\newcommand{\vladimir}{\textbf{Vladimir}}
\newcommand{\anton}{\textbf{Anton}}
\newcommand{\alexandr}{\textbf{Alexandr}}
\newcommand{\vasily}{\textbf{Vasily}}
\newcommand{\dmitrii}{\textbf{Dmitrii}}
	
\begin{document}
	
	
\begin{center}
	{\bf\Large Report : Strain dependence on exchange interaction}\\
	{\bf\Large \today}\\
	\vspace{0.4cm}
	{\large Valentin \textsc{Besse}\footnote{Author of the report}, Vladimir \textsc{Vlasov}, Anton \textsc{Golov}, Alexandr \textsc{Alekhin}, Dmitrii \textsc{Kuzmin} and Vasily \textsc{Temnov}}\\
	\vspace{0.6cm}
	%{\large \today}
	%{\large August 28, 2017}
\end{center}
\vspace{0.1cm}

\section*{Version}

\begin{itemize}
    \item February 22, 2018: V1.
\end{itemize}

\section{Introduction}

In this report we discuss the strain dependence of the exchange interaction. 
We present the theory that describe the energy and the field of the exchange interaction (see section \ref{sec1}).
We introduce the strain dependence on these equations and we predict some results.

We conclude by a proposition of the new tasks regarding this specific interaction.

\section{Theory}
\label{sec1}

The energy of the exchange interaction in a ferromagnet can be represented by \cite{gurevich1996magnetization}
\begin{equation}
    U_{\mathrm{ex}} = U_{\mathrm{ex,0}} + U_{\mathrm{ex,NU}}
    \label{eq1}
\end{equation}
where $U_{\textrm{ex,0}}$ is the exchange energy when the magnetization is uniform and $U_{\textrm{ex,NU}}$ is responsible for the change of the exchange energy when the magnetization is non-uniform.
The first term of Eq. \eqref{eq1} can be written
\begin{equation}
    U_{\mathrm{ex,0}} = \frac{1}{2} \mathbf{M} \overleftrightarrow{\Lambda} \mathbf{M}
    \label{eq2}
\end{equation}
with the magnetization $\mathbf{M}$ and the exchange tensor $\overleftrightarrow{\Lambda}$.

The second term of Eq. \eqref{eq1} can be written
\begin{equation}
    U_{\mathrm{ex,NU}} = \frac{1}{2} \sum_{p=1}^3 \sum_{s=1}^3 q_{ps} \frac{\partial \mathbf{M}}{\partial x_p} \frac{\partial \mathbf{M}}{\partial x_s}
    \label{eq3}
\end{equation}
where $q_{ps}$ are the components of a tensor $\overleftrightarrow{q}$.

The effective field is a functional derivative (or variational derivative) of the energy by the magnetization vector
\begin{equation}
    H_{\mathbf{eff}} = - \frac{\delta U}{\delta \mathbf{M}} = - \frac{\partial U}{\partial \mathbf{M}} + \sum_{p=1}^3 \frac{\partial}{\partial x_p} \left[ \frac{\partial U}{\partial \left(\partial \mathbf{M} / \partial x_{p} \right)} \right]
    \label{eq4}
\end{equation}
with the total free energy $U$.
Using Eqs. \eqref{eq3} and \eqref{eq4} we obtain the contribution of the exchange interaction to the effective field
\begin{equation}
    \mathbf{H}_{\mathrm{ex}} = \mathbf{H}_{\mathrm{ex,0}} + \mathbf{H}_{\mathrm{ex,NU}} \equiv \overleftrightarrow{\Lambda} \mathbf{M} + \sum_{p=1}^3 \sum_{s=1}^3 q_{ps} \frac{\partial^2 \mathbf{M}}{\partial x_p \partial x_s}
    \label{eq5}
\end{equation}

So now, let's consider the case of an isotropic ferromagnet, it implies that $\Lambda$ and $q$ are scalars.
We write $q = D$.
We also consider the equation only for the x-direction.
The Eq. \eqref{eq5} becomes
\begin{equation}
    \mathbf{H}_{\mathrm{ex}} = \Lambda \mathbf{M} + D \frac{\partial^2 \mathbf{M}}{\partial x^2}.
    \label{eq6}
\end{equation}
We write the magnetization vector as a Fourier series
\begin{equation}
    \mathbf{M} = \mathbf{M}_0 + \sum_{n=0}^N \mathbf{M}_n \left( t \right) \cos \left( k_n x\right)
    \label{eq7}
\end{equation}
where $\mathbf{M}_0$ is the steady states of the magnetization vector, $\mathbf{M}_n$ is the n-th order of the magnetization vector and $k_n$ is the wavevector of the n-th magnetic order.
It implies that $\mathbf{M}_n \ll \mathbf{M}_0$.
Substitutes Eq. \eqref{eq7} into the non-uniform part of Eq. \eqref{eq6} we obtain 
\begin{equation}
    \mathbf{H}_{\mathrm{ex,NU}} =  D \frac{\partial^2 \mathbf{M}}{\partial x} = - D \sum_{n=0}^N k^2_n \mathbf{M}_n^2 \cos \left( k_n x\right).
    \label{eq8}
\end{equation}
The lossless Landau-Lifshitz-Gilbert equation is defined by
\begin{equation}
    \frac{\partial \mathbf{M}}{\partial t} = - \gamma \mathbf{M} \times \mathbf{H}_{\mathrm{eff}}
    \label{eq9}
\end{equation}
with $\gamma$ is the gyromagnetic ratio.
It is obvious that since $\mathbf{H}_{\mathrm{ex,0}}$ depends on $\textbf{M}$ so it does not play a role $$\mathbf{M} \times \mathbf{H}_{\mathrm{ex,0}} =0.$$
Adding Eq. \eqref{eq8} into Eq. \ref{eq9} we obtain
\begin{equation}
    \frac{\partial \mathbf{M}}{\partial t} + \gamma D \left[ \mathbf{M} \times \frac{\partial^2 \mathbf{M}}{\partial x^2} \right] = 0
    \label{eq10}
\end{equation}
Let's consider that the time dependence of the magnetization vector is $$\mathbf{M} \left(t, \mathbf{r} \right) \sim \mathbf{M} \left( \mathbf{r} \right) \exp \left( i \omega t \right)$$ and that the exchange constant $D$ is modified by the propagation of a strain: the distance between two atoms changes.
So the exchange coefficient depends on time and space.
\begin{equation}
    i \omega \mathbf{M} + \gamma D \left( t, z \right) \left[ \mathbf{M} \times \frac{\partial^2 \mathbf{M}}{\partial x^2} \right] = 0
    \label{eq11}
\end{equation}
The Eq. \eqref{eq11} shows that the exchange interaction appears only in parametric terms.
It means that this term cannot drive the magnons by itself if $\mathbf{M}_n \left( t = 0, \mathbf{r} \right) = \overrightarrow{0}$.

Now, let's consider that the exchange coefficient is dependant on strain ($\epsilon$) propagation.
We write
\begin{equation}
    D \left( t, z \right) \sim D_{0} \exp \left( -\frac{\Delta r}{R_{\mathrm{D}}} \right)
    \label{eq12}
\end{equation}
where $D_0$ is the exchange coefficient equilibrium value at the equilibrium, $\Delta r$ is the distance between two neighbor electrons which depends on the strain and $R_{\mathrm{D}}$ is the typical length of the screening effect.
The distance between two neighbor electrons change proportionally to the amplitude of the strain $$ \Delta r \sim r_0 \epsilon$$
where $r_0$ is the distance between two neighbor electrons at the equilibrium.
The Eq. \eqref{eq12} is
\begin{equation}
    D \left( t, z \right) \sim D_{0} \exp \left( -\frac{r_0 \epsilon}{R_{\mathrm{D}}} \right)
    \label{eq13}
\end{equation}
We develop in Taylor series the Eq. \eqref{eq13}
\begin{equation}
    D \left( t, z \right) \sim () D_{0} \left( 1 + \frac{r_0}{R_{\mathrm{D}}} \epsilon \right).
    \label{eq14}
\end{equation}
The typical length of the screening effect is in the range of the size of the lattice $r_0$.
Consequence Eq. \eqref{eq14} is
\begin{equation}
    D \left( t, z \right) \sim D_{0} \left( 1 + \epsilon \right).
    \label{eq15}
\end{equation}
So the first-order Taylor coefficient is in the order of the strain amplitude, so typically from $0.01 \%$ to $0.1\%$.

\section{Conclusion}

In conclusion, the exchange interaction cannot drive the magnons by itself.
It is necessary to consider it along with the magnetoelastic effect or to use a non-zero initial value for magnetization vector.
Also it appears that the Taylor expansion's first-order coefficient of the exchange interaction is in the range of the amplitude of the strain (from $0.01 \%$ to $0.1\%$).

\newpage

\section*{List of abbreviations}

\begin{table}[ht]
    %\centering
    \begin{tabular}{ l c r }
        Landau-Lifschitz-Gilbert & $\Longrightarrow$ & LLG \\
        Ferromagnetic resonance & $\Longrightarrow$ & FMR \\
    \end{tabular}
\end{table}

\bibliographystyle{ieeetr}
\bibliography{Exchange_Magnons}

\end{document}